Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-12-02 writeups/dissertation/dissertation.tex
foo

\def\committee{
  Michael D. Byrne, Chair \\
  Professor, Psychology and Computer Science \and
  Phillip Kortum \\
  Assistant Professor, Psychology \and
  Devika Subramanian \\
  Professor, Computer Science and Electrical Engineering \\
}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{descr-tagFrequencyCount.pdf}}}
  \caption{
    Log-log plot of tag frequency versus rank for the StackOverflow dataset and Twitter popular-users and popular-hashtags dataset subsets.
    Rank was assigned to each unique tag after ordering by tag frequency (most frequent given smallest rank).
}
  \label{figDescTagFreq}
\end{figure}

>>>>

\def\committee{
  Michael D. Byrne, Chair \\
  Professor, Psychology and Computer Science \and
  Philip Kortum \\
  Assistant Professor, Psychology \and
  Devika Subramanian \\
  Professor, Computer Science and Electrical Engineering \\
}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{descr-tagFrequencyCount-crop.pdf}}}
  \caption{
    Log-log plot of tag frequency versus rank for the StackOverflow dataset and Twitter popular-users and popular-hashtags dataset subsets.
    Rank was assigned to each unique tag after ordering by tag frequency (most frequent given smallest rank).
}
  \label{figDescTagFreq}
\end{figure}
